Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
corrections to experiment design section

\subsection{Censorship} %%%
% \indent \indent Motivational paragraph time about how this is so everywhere.

@@

We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
demographics of our participants, open-ended responses of their experience with censorship circumvention,
and general security questions to gauge their awareness in this area. Along with the empirical measurements 
we have taken during the experiment, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.

@@

\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thus require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{\bfseries Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
%what do users need to do to circumvent this? 
\item{\bfseries DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
%what do users need to do to circumvent this? 
\item{\bfseries Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
%what do users need to do to circumvent this? 
\end{itemize}

@@

\subsection{Web Browsing Tasks}
\indent \indent The tasks below are designed to be easy and quick to complete for an average
computer user. This design is critical since the objective of the experiment is to observe
how comfortable users are with circumventing censorship, which we indirectly measure
by taking data regarding how participants complete the task. Giving participants tasks 
they are not comfortable with performing or sending them to websites which they are 
unfamiliar with will introduce more variables into the experiment to account for. 
Specifically, we would need to separate any confusion caused by the task itself versus
the task of circumventing censorship.

@@

We plant to solicit feedback on the design of this experiment at HotPETs 2015. 
Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\subsection{Recruitment}  
\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
does not keep information regarding its user base, we will try to obtain a user base representative of
the average Internet using-population. Additionally, recruiting a large number of participants has the 
benefit of ensuring enough samples in order to have significant effect sizes in 
each simulated censorship environment.

@@

We also take this time to and collect feedback on the experience as a whole and the usability of 
the Tor Browser. Out of the five questions, there are two multiple choice questions and three 
open-ended feedback questions in which our participants can write us any length of response. 
We opted for both concrete quantitative measurements of their experience along with free-text
qualitative data to gather a broad range of information from our 200 participants in a scalable manner.

\subsection{Empirical Data} 
Although quantitative and qualitative data provides valuable feedback into what users perceive of 
their censorship circumvention experience, it will be imperative that we check for the validity of their 
statements by analyzing empirical data collected by our browser extension during the process of the
experiment. Specifically, we will capture:

>>>>

\subsection{Censorship}

@@

We will end the experiment with a survey of 17 questions in order to collect basic participation information, 
demographics of our participants, open-ended responses of their experience with censorship circumvention,
and general security questions. Along with the empirical measurements, we will use this survey information to determine which configuration tasks are hard (bridges versus proxies), how many were successful, how long it took users to configure, if they understood the process, and if they were confident that it was working as expected.

@@

\indent \indent We plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thus require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{\bfseries Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{\bfseries DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{\bfseries Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

@@

\subsection{Web Browsing Tasks}
\indent \indent The tasks below are designed to be easy and quick to complete for an average
computer user. This design is critical since the objective of the experiment is to observe
how comfortable users are with circumventing censorship, which we indirectly measure
by taking data regarding how participants complete the task. Giving participants tasks 
they are not comfortable with performing or sending them to websites which they are 
unfamiliar with will introduce more variables into the experiment. 
Specifically, we would need to separate any confusion caused by the task itself versus
the task of circumventing censorship.

@@

We plant to solicit feedback on the design of this experiment at HotPETs 2015. 
We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\subsection{Recruitment}  
\indent \indent We plan to recruit around 200 users for the purpose of this study, making this the largest user 
study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
does not keep information regarding its user base, we will try to obtain a user base representative of
the average Internet using-population. Additionally, recruiting a large number of participants has the 
benefit of ensuring enough samples in order to have significant effect sizes in 
each simulated censorship environment.

@@

We also take this time to and collect feedback on the experience as a whole and the usability of 
the Tor Browser. Out of the five questions, there are two multiple choice questions and three 
open-ended feedback questions in which our participants can write us any length of response. 
We opted for both concrete quantitative measurements of their experience along with free-text
qualitative data to gather a broad range of information in a scalable manner.

\subsection{Empirical Data} 
Although quantitative and qualitative data provides valuable feedback into what users perceive of 
their censorship circumvention experience, we will check for the validity of their 
statements by analyzing empirical data collected by our browser extension during the process of the
experiment. Specifically, we will capture:
